\problemname{Undetermined Determinant}

Two of the classes freshmen at the University of Texas often take are
linear algebra and discrete math. The former teaches vectors, matrices, and
operations on them, while the latter covers a variety of topics including
combinatorics and graph theory.

John is a freshman at UT, and it is finals season. His professors gave study
guides for their final exams, and one of the bullet points in the linear
algebra study guide is the following:

\begin{itemize}
    \item Given a matrix, you should be able to compute its determinant.
\end{itemize}

Here's a bullet point in the discrete math study guide:

\begin{itemize}
    \item Given a graph, you should be able to write down its adjacency matrix.
\end{itemize}

In the course of his studying, John realized that these problems can be
combined naturally: given a graph, compute the determinant of its adjacency
matrix. After solving this problem a few times, John began to grow bored, and
he wondered if he could find some information about the answer to this question
for a whole class of graphs. He wrote the following question on a blank page
in his notebook before going to sleep:

\begin{itemize}
    \item Given a positive integer $N$, consider a uniform random labeled tree
        on $N$ vertices. What is the expected value of the determinant of its
        adjacency matrix?
\end{itemize}

Now John is asleep and the problem is haunting his dreams. Can you help him
solve it?

It can be shown that the answer is a rational number that can be written in
the form $p/q$, with $q \not\equiv 0 \pmod{998\,244\,353}$. You should output
your answer as an integer in $[0, 998\,244\,353)$ equivalent to $pq^{-1}$
modulo $998\,244\,353$.

\section*{Definitions}

A tree on $N$ vertices is a connected undirected graph with $N$ vertices and
$N - 1$ edges. A labeled tree is one whose vertices are labeled with the
integers $1, \dots, N$. Two labeled trees are distinct if they do not have the
same set of edges, where an edge is defined as an unordered pair of integers in
$\{1, \dots, N\}$. Note that two distinct labeled trees may have the same
structure, but different vertex labelings.

\section*{Input}

The input consists of a single line containing a single integer, $N$
($1 \leq N \leq 10^6$), the number of vertices in the uniform random labeled
tree.

\section*{Output}

Output a single integer in $[0, 998\,244\,353)$, the answer to the problem
as a rational number modulo $998\,244\,353$.
