\problemname{Leaky Cauldron}

In a faraway magical land, there exists a very large cauldron. Unfortunately, it is leaking today!
The cauldron holds a massive amount of water, but is leaking onto a rectangular stone area.
The cauldron is floating right above the center square of the stone area, and over time, the leaked water
will spread from the center square outward.

Different parts of the rectangular stone area vary in height. The stone area can be broken up into an $N$
by $M$ grid, with each square in the grid potentially having a different height. The water flows down into
the center square of the grid (which is guaranteed to have the lowest height). After $h$ seconds, the water
level in the center square will be at height $h$. Once the water level reaches height $h$, any squares that
have height $h$ or below that are connected to the center square by already submerged squares will be
covered with water. Thus, as the water level gradually rises, more squares become submerged. This water is
magic; it will instantly expand to submerge adjacent squares with height less than the height of the water,
so don't worry about the rate of flow from the cauldron.

At every second up until $H$ seconds, find the area of the largest sub-rectangle in the $N$ by $M$ grid that 
is completely submerged by water. That is, every square of the rectangle should be covered by water for the
rectangle to qualify.

\section*{Input}
On the first line, there will be $3$ integers $N$, $M$, and $H$ respectively, with $1 \le N, M < 200$
and $1 \le H \le 2\,500$. Then, the following $N$ lines will each contain $M$ space separated integers,
each with a single height $h$, where $0 \le h \le H$, giving the heights of the $N$ by $M$ grid.
It is guaranteed that $N, M$ are odd. The height of the center square will always be $0$, and it will
always be the lowest in the grid.

\section*{Output}
$h + 1$ lines, where the $i^\textrm{th}$ line is the area of the largest rectangle of water when the water height has reached height $i$ in the middle square. 
