\problemname{Pigeon X}

\begin{center}
\textit{
$M$ bad pigeons in a mansion \\
Wrist on Milly Rock them diamonds on me dancin' \\
When you workin' hard then your money start expandin' \\
I got model pigeon wanna peck me like some candy \\
And them seeds come in handy \\
Last name Savage pigeon, no I'm not Randy \\
}
\end{center}

21 Savage has $M$ bad pigeons in a mansion with $N$ rooms. Each pigeon
is in a different room. He also has $M$ seed stashes stored in rooms across
the mansion. The mansion can be represented as a weighted undirected graph
where each room is a node and each corridor is an edge between two nodes. 21
Savage desires to pair pigeons with a seed stash so that the total distance
each pigeon has to travel to reach its seed is minimized.

\medskip

Help 21 Savage match pigeons with seed!

\section*{Input}

The first line of input has two space separated integers $N$ and $M$, the
number of rooms and the number of pigeons and seed stashes. It is guaranteed
that $1 \le N \le 500$ and $1 \le 2M \le N$.

$N$ lines follow. Each line has $N$ space separated integers. The $j$th entry
on the $i$th line represents the length of the corridor from room $i$ to room
$j$. It is guaranteed that the length of the corridor from room $i$ to room
$j$ is the same as the length of the corridor from room $j$ to room $i$. It
is also guaranteed that the length of the corridor from room $i$ to room $i$
for all $i$ is $0$.

The next line has $M$ space separated unique integers representing the room
locations of the $M$ pigeons. It is guaranteed that all integers $F_i$ satisfy
$0 \le P_i < N$.

The final line has $M$ space separated unique integers representing the room
locations of the $M$ seed stashes. It is guaranteed that all integers $F_i$ satisfy
$0 \le F_i < N$.

\section*{Output}

Output a single integer, the minimum total distance that all pigeons have to
travel to eat a unique seed stash.
