\problemname{Bump, Set, Spike!}

Volleyball season is starting at your local recreational center! This means all kinds of volleyball
leagues are about to be in full swing: leagues for youths, seniors, amateurs, and so on. The most
prestigious and highly contested league at the rec center is the Premier Adult Coed Volleyball
League. In recent years, the prestige of the league has become problematic, as all the top referees
have opted to shirk their duties and compete as players, leaving only sub-par referees to oversee
league matches.

To combat this, league organizers have proposed the possibility of a program that can play the role of
referee. More specifically, for each rally, a sequential record of who touches the ball is streamed to
the program, and from that it should be determined in real-time if there are any violations of the
following rules:

\begin{enumerate}
    \item A player cannot touch the ball twice in a row.
    \item A team cannot touch the ball more than three times in a row.
    \item If a team touches the ball twice or more before it is hit to the other team, both a man
    and a woman must have touched the ball at least once.
\end{enumerate}

Other violations, such as net touches, carries, or the ball landing out of bounds will still be called
by human referees, so the program need not worry about those.

The league organizers have come to you for help in creating this program. The ball is in your court!

\section*{Input}

The first line contains a single integer $N$ $(2 \leq N \leq 10^5)$, the number of touches in the rally. 
Then follows $N$ lines, with the $i$th line describing the $i$th touch in the rally. Each of the $N$ lines
will contain a string consisting of three characters. The first character will be either \texttt{A} or
\texttt{B}, denoting the team that touched the ball. The second character will be one of \texttt{1},
\texttt{2}, \texttt{3}, \texttt{4}, \texttt{5}, or \texttt{6}, denoting the specific player on the team that
touched the ball. The final character will be either \texttt{W} or \texttt{M}, denoting whether the player
that touched the ball was a man or a woman.

\section*{Output}

If there was a violation in the rally, print either \texttt{A} or \texttt{B}: whichever team was first to
commit a violation. If there was no violation, print \texttt{No violation}.
