\problemname{Candy Consumption}

Kevin loves to eat all types of candy: chocolate, hard candy, jelly beans, gummy bears, and so on.
There are $N$ different types of candy that he is particularly enamored of at the moment, and unfortunately
for his dentist, he maintains a virtually unlimited stash of each type.

Kevin considers himself something of a candy connoiseur; he is very particular about how he consumes his
candy. He finds that variability in the sequence of candies that he eats is extremely important, as
different qualities of the candies are really highlighted by certain sequences. For example, eating gummy
bears after hard candy really accentuates the chewy texture, whereas eating jelly beans after eating dark
chocolate really brings out the sweetness and flavor of the jelly beans. Knowing this, Kevin has devised the
following procedure for eating the $N$ types of candy he currently enjoys. He selects a candy from amongst
the $N$ types at random, and eats a candy of that type. He then repeats, continuing to randomly select and
consume a candy until he eats a candy type that he has eaten previously. Once he has repeated a candy
type, he finds that the sequence's variability has been ruined, so he stops. Kevin calls this ordered
sequence of candies that he has eaten a Candy Consumption Sequence. For example, say he randomly chooses
to eat chocolate, then jelly beans, then hard candy, then gummy bears, then chocolate again. This is a
Candy Consumption Sequence with 5 total candies.

Kevin realizes that there are a finite number of unique Candy Consumption Sequences. If he consumes all the
candies for every possible unique Candy Consumption Sequence, how many total candies will he have eaten? 
Since this answer may be very large, output its remainder modulo the prime $1000000007$.

\section*{Input}
The first line contains a single integer $N$ ($1 \leq N \leq 10^6$).

\section*{Output}
Output a single integer representing the number of candy consumed over all possible Candy Consumption
Sequences, modulo $1000000007$.
