\problemname{Red Light, Green Light}

A recent study has shown that long commutes can have negative effects on one's happiness. Upon reading
this study, Jay had suddenly become quite unhappy with his long commute to work; it seems the study is
true after all. Jay now has frequent dreams in which he has a short daily commute, and these pleasant
dreams often cause Jay to sleep through his alarms in the morning.

On the day of his Very Important Meeting, Jay once again oversleeps, to his dismay. As he leaves his house
at time $0$, he realizes he only has $T$ minutes to reach his workplace. The city Jay works in contains
$N$ intersections (labeled $1$ to $N$) and $M$ one-way roads between intersections that vary in length.
His house is located at intersection $1$, and his workplace is located at intersection $N$.

The real culprits responsible for Jay's long commute are the traffic lights that are located on every road.
Jay has driven around the city so much that he's realized that each light operates on a cycle: for the $i$th
road, the light is green for $g_i$ minutes, then red for $r_i$ minutes, then green for $g_i$ minutes, and so 
on. Jay has also figured out the specific values of $g_i$ and $r_i$ for every road in the city, and he has
calculated the first time $t_i$ after time $0$ (when Jay leaves his house) that each road's traffic light is
green. Here, $t_i$ will fall somewhere in the inclusive range $[0, r_i]$. Jay can only take a road if the
light is green; otherwise, he must wait at the intersection or choose to take a different road. Once he
enters a road, he can continue to the end even if the light turns red before he reaches the next
intersection.

While Jay wants to make it to his meeting on time, he also wants to avoid driving too fast. Knowing all
this information about the city's traffic lights, Jay wants to know the minimum speed he needs to drive
in order to make it to his meeting in time.

\section*{Input}

The first line of input contains three space-separated integers, $N$ ($2 \leq N \leq 50000$), $M$
($1 \leq M \leq 50000$), and $T$ ($1 \leq T \leq 10^6$). Then follows $M$ lines, the $i$th of which
describes the $i$th road in the city. Each of the $M$ lines will contain six space-separated integers,
$u_i$, $v_i$ ($1 \leq u_i, v_i \leq N$), $l_i$ ($1 \leq l_i \leq 10^6$), $g_i$, $r_i$
($1 \leq g_i, r_i \leq 10^4$), $t_i$ ($0 \leq t_i \leq r_i$), denoting that the $i$th road is from
intersection $u_i$ to intersection $v_i$, has a length of $l_i$ feet, and the period of the road is
described by $g_i$, $r_i$, and $t_i$ (as explained in the statement above). There will be at most one road
from city $u$ to city $v$ for all $u$, $v$, and there will be no roads from a city to itself (note that
there may be a road from $u$ to $v$ AND $v$ to $u$).

It is guaranteed that Jay will be able to reach his workplace from home.

\section*{Output}

Output the minimum speed Jay needs to drive in feet per minute in order to reach his Very Important Meeting
on time. Answers within a relative or absolute error of $10^{-6}$ will be accepted.
