\problemname{Uzbek Trek}

Traveler Todd plans on making the trek from Kazakhstan to Turkmenistan.
In order to do so, he must navigate through the great nation of Uzbekistan.

\medskip

Unfortunately, Uzbekistan imposes a tax on all foreign travelers who pass
through it. Uzbekistan has imposed a particularly peculiar tax on Todd.
While trekking through Uzbekistan, Todd must wear special shoes with the
blue, white and green flag of Uzbekistan stiched onto them. Each
shoe only lasts for a certain amount of footsteps. Specifically, the $k$th type of shoe
lasts for exactly $p^k$ footsteps, where $k \ge 0$ and $p$ is some predetermined value.

\medskip

Being the prepared traveler he is, Todd calculates that it will take him $n$ footsteps to travel through
Uzbekistan. He then goes to the Uzbek Shoe Depot where he plans to purchases all
the shoes he needs to complete his journey. The Uzbek Shoe Depot is a luxury store,
so Todd can order as many shoes as he likes.
For each shoe that Todd orders, he specifies the type $k$ of shoe that he wants.
Todd would hate to waste the durability of his purchased shoes;
help him determine how many ways he can order sets of shoes so
that he can wear all the shoes in sequence to travel \textbf{exactly} $n$
footsteps! The answer may be large, so output its remainder modulo $10^9 + 7$.

\medskip

Note that two sets of shoes are considered the same if they have the same
number of shoes of each type. It does NOT matter what order Todd wears the
shoes in.

\section*{Input}
The first line contains space-separated integers $n$ and $p$ such that
$1 \leq n \leq 10^9$ and $10^2 \leq p \leq 10^9$.

\section*{Output}
Output a single integer, the number of unique sets of shoes Todd can order
to travel exactly $n$ steps. Since the answer can be large, output it modulo $10^9 + 7$.
