\problemname{Con-cat-nation}

In Catopolis, there is a widely held belief that their neighbor, Pupridge, is preparing to invade. The coolest cats have decided to send their best concats into Pupridge as spies, however there is a problem. Pupridge has a bullet-proof identification scheme: every pet seeking entry must present an id (string). The Border Collies check that the id's length is within allowed bounds, and that every character is followed by an allowed successor. 

More specifically, the Border Collies have an minimum allowed length $x$, maximum allowed length $y$, and, for each character $c$, a list of characters that are allowed to follow $c$. (if a character is the last character of the id, they don't check for the next character). For example, if the only character allowed to follow "a" is "a", then "aaaaa" is valid, while "az" is not, as "z" follows "a."

As cats don't have opposable thumbs they can't type, so they can't forge ids!

\medskip

Of course, the crafty cats have found a workaround: they can use a scanner and printer to append a fellow cat's id to their own! However resources are scarce, each cat can only append one id to their own, and this id has to be from one of their fellow cat's. (Note that they are allowed to append a copy of their own id).

\medskip

For each cat, it is your job to figure out if they can pass verification.

Ids are only made of the latin lowercase characters a through z.

\section*{Input}
On the first line, $n, x, y$, the number of cats, minimum allowed length of the id, and the maximum allowed length of the id respectively. $1 \leq N \leq 10^5$, $0 \leq x \leq y \leq 20$.
26 lines follow, denoting the valid successors of the characters "a,b,c,...z" respectively. Each line has the format $x s$, where $x$ is the number of valid successors and $s$ is a string containing all of the valid successors.
$n$ lines follow each containing a string $id_i$, $1 \leq |id_i| \leq 20$ denoting the id of the $i$th cat.

\section*{Output}
$n$ lines, the $i$th of is either "Feline good!" if the cat can pass verification, or "Get meowt!" if they cannot.
