\problemname{Bump, Set, Spike, Count!}

Volleyball season is starting at your local recreational center! This means all kinds of volleyball
leagues are about to be in full swing: leagues for youths, seniors, amateurs, and so on. The most
prestigious and highly contested league at the rec center is the Premier Adult Coed Volleyball
League. A volleyball match in the Premier Adult Coed Volleyball League is played between $2$ teams of
$6$ players. In recent years, the prestige of the league has become problematic, as all the top referees
have opted to shirk their duties and compete as players, leaving only sub-par referees to oversee
league matches.

Since league organizers have already solved the problem of determining if a set of touches is valid,
league organizers have now set their sights on a different problem. More specifically, they want to
calculate the number ways to construct a valid sequence of touches of size $N$.

In addition, the referees have determined to be lax in terms of the rules for a valid set of touches.
A set of touches is valid if:

\begin{enumerate}
    \item A player cannot touch the ball twice in a row.
    \item A team cannot touch the ball more than three times in a row.
\end{enumerate}

Other violations, such as net touches, carries, or the ball landing out of bounds will still be called
by human referees, so the program need not worry about those.

The league organizers have come to you for help. The ball is in your court!

\section*{Input}

The input consists of a single integer $N$ $(0 \leq N \leq 10^4)$.

\section*{Output}

Output the number of ways to constuct a valid sequence of touches of size $N$. Since the output may be
large, output it modulo $10^9 + 7$.
